### 2014-08-05 analysis/figures/paper_figures.tex
Added control version of figure 2.

\setcounter{figure}{1}

\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
\end{tabular}
\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
\end{center}
\end{figure}

>>>>

\setcounter{figure}{1}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_12_15_47_vep_ctr-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_25_22_vep_-crop.pdf}} \\
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_26_26_ssaep_ctr_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_42_15_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_13_26_ssvep_ctr_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_23_01_ssvep_40-crop.pdf}}
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
\end{tabular}
\caption{Live control trials. At Basilar Tip. NOTE: This is a different location for rabbit 10. NOTE: Does not exist for rabbit 8.} % Figure 2
\end{center}
\end{figure}

\setcounter{figure}{1}
\begin{figure}[H]
\begin{center}
\begin{tabular}{cccc}
& Rabbit 10 & Rabbit 9 & Rabbit 8 \\
\raisebox{-0.5\height}{\rotatebox{90}{VEP}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_11_57_42_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_15_05_2014_14_13_26_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Tue_06_05_2014_11_17_10_vep_-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../vep/matlab_data/_Thu_24_04_2014_12_55_56_vep_-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSAEP 86 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_31_02_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_26_54_ssaep_86-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_37_22_ssaep_86-crop.pdf}} \\
\raisebox{-0.5\height}{\rotatebox{90}{SSVEP 40 Hz}} &
%\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_12_08_22_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_15_05_2014_14_20_24_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Tue_06_05_2014_11_14_51_ssvep_40-crop.pdf}} &
\raisebox{-0.5\height}{\includegraphics[scale=0.10]{../ssavep/matlab_data/_Thu_24_04_2014_12_59_49_ssvep_.pdf}}
\end{tabular}
\caption{At Basilar Tip for rabbit 8 and 9; at mid-basilar for rabbit 10.} % Figure 2
\end{center}
\end{figure}
